LAGOS lake depth

### 2019-06-03 lagos_depth.Rmd
compute some summary stats

```{r message=FALSE}
library(LAGOSNE)
library(ggplot2)
library(sf)
library(dplyr)

lg       <- lagosne_load("1.087.1")
lg_depth <- dplyr::select(lg$lakes_limno, 
                          lagoslakeid, maxdepth, maxdepthsource) %>% 
  left_join(lg$locus, by = "lagoslakeid") %>%
  dplyr::filter(!is.na(maxdepth)) %>%
  coordinatize()
```

```{r viz}
hist(lg_depth$maxdepth)
knitr::kable(t(quantile(lg_depth$maxdepth, c(0, 0.05, 0.5, 0.95, 1))))

```

>>>>

```{r data, message=FALSE}
library(LAGOSNE)
library(ggplot2)
library(sf)
library(dplyr)

lg       <- lagosne_load("1.087.1")
lg_depth <- dplyr::select(lg$lakes_limno, 
                          lagoslakeid, maxdepth, maxdepthsource) %>% 
  left_join(lg$locus, by = "lagoslakeid") %>%
  mutate(has_limno = lagoslakeid %in% lg$epi_nutr$lagoslakeid) %>%
  # dplyr::filter(!is.na(maxdepth)) %>%
  coordinatize()
```

```{r viz}
hist(lg_depth$maxdepth)
knitr::kable(t(quantile(lg_depth$maxdepth, c(0, 0.05, 0.5, 0.95, 1), 
                        na.rm = TRUE)))

paste0(round(sum(!is.na(lg_depth$maxdepth)) / nrow(lg_depth) * 100, 2),
       "% of lakes have maxdepth values.")

paste0(round(sum(!is.na(dplyr::filter(lg_depth, has_limno)$maxdepth)) / 
  length(unique(lg$epi_nutr$lagoslakeid)) * 100, 2), 
  "% of lakes with limno data have maxdepth values.")

paste0(round(sum(dplyr::filter(lg_depth, !is.na(maxdepth))$lagoslakeid %in% 
            lg$epi_nutr$lagoslakeid) / 
        nrow(lg_depth) * 100, 2), 
       "% of lakes with maxdepth values have limno data.")

ggplot() + 
  geom_sf(data = LAGOSNE::lg_extent) +
  geom_sf(data = dplyr::sample_frac(lg_depth, 0.2), 
          aes(color = cut(maxdepth, round(quantile(maxdepth, c(0, 0.05, 0.5, 0.95, 1), 
                                                   na.rm = TRUE)))), 
          size = 1, alpha = 0.4, shape = 21) +
  scale_color_viridis_d(direction = -1) +
  coord_sf(datum = NA) + theme_void() +
  labs(color = "depth (m)")
```
